Enhancement of SDR in Thessaloniki Clear Sky

### 2024-05-09 GHI_enh_CSid.tex
Commit 2024-05-09 12:14

  pdftitle={Enhancement of SDR in Thessaloniki},

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-08}

@@

$objective
[1] 8644.06
\end{verbatim}

@@

\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}

\CommentTok{\# plot(  DTyear[, glo, year],}
\CommentTok{\#        ylim = ylim)}
\CommentTok{\# points(DTyear[, GLB, year], col = "green")}

\FunctionTok{plot}\NormalTok{(DTyear[, N, year], }\AttributeTok{col =} \StringTok{"blue"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, GLB}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / Clear Global yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Ref}\SpecialCharTok{/}\NormalTok{glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Threshold ref / CS libratran yearly means"}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(DTyear[, Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"Threshold / global yearly means"}\NormalTok{, trend\_factor))}

\NormalTok{ff }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x) \{}
    \FunctionTok{plot}\NormalTok{(DTyear[, }\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{, }\AttributeTok{main =}\NormalTok{ x)}
\NormalTok{    DTyear[, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{abs}\NormalTok{(}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ x }\SpecialCharTok{*}\NormalTok{ Thr}\SpecialCharTok{/}\NormalTok{GLB))]}
\NormalTok{\}}

\FunctionTok{optimize}\NormalTok{(ff, }\FunctionTok{c}\NormalTok{(.}\DecValTok{5}\NormalTok{, }\FloatTok{1.5}\NormalTok{), }\AttributeTok{tol =} \FloatTok{0.001}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$minimum
[1] 0.8590668

$objective
[1] 0.6771877
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ff}\NormalTok{(}\FloatTok{0.85}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 0.7037762
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(DTyear[, GLB, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, Thr, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, glo, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(DTyear[, Ref, year], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}

\FunctionTok{rmserr}\NormalTok{(DTyear}\SpecialCharTok{$}\NormalTok{GLB, DTyear}\SpecialCharTok{$}\NormalTok{Thr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
$mae
[1] 97.55895

$mse
[1] 9799.437

$rmse
[1] 98.9921

$mape
[1] 0.1680595

$nmse
[1] 46.16276

$rstd
[1] 0.1700543
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DTmonth }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                    \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
                    \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
\NormalTok{                    .N),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date), }\FunctionTok{month}\NormalTok{(Date))]}
\NormalTok{DTmonth[, tsy }\SpecialCharTok{:=}\NormalTok{ year }\SpecialCharTok{+}\NormalTok{ (month }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)}\SpecialCharTok{/}\DecValTok{12}\NormalTok{ ]}

\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTmonth[, glo, GLB])}

\CommentTok{\# plot(  DTmonth[, glo, tsy],}
\CommentTok{\#        ylim = ylim)}
\CommentTok{\# points(DTmonth[, GLB, tsy], col = "green")}

\CommentTok{\# plot(  DTmonth[, .N, tsy], col = "blue")}
\FunctionTok{plot}\NormalTok{(  DTmonth[, GLB}\SpecialCharTok{/}\NormalTok{glo, tsy], }\AttributeTok{col =} \StringTok{"red"}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\StringTok{"Clear GLB / CS libratran by month"}\NormalTok{)}

\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{out.height =} \StringTok{"32\%"}\NormalTok{   )}

\NormalTok{Ratio\_lim }\OtherTok{\textless{}{-}} \FloatTok{0.85}

\NormalTok{DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, .N]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(}\FunctionTok{c}\NormalTok{(DTdaily[GLB\_Sum}\SpecialCharTok{/}\NormalTok{glo\_Sum }\SpecialCharTok{\textless{}}\NormalTok{ Ratio\_lim, Day]))}

\NormalTok{days }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(DTdaily[, Day], }\DecValTok{40}\NormalTok{)}

\CommentTok{\# for (ad in sort(days)) \{}
\CommentTok{\#   temp \textless{}{-} DATA[Day == ad,]}
\CommentTok{\#}
\CommentTok{\#   ylim \textless{}{-} range(temp[, Low\_B.Low\_W.glo, wattGLB])}
\CommentTok{\#}
\CommentTok{\#   plot(  temp[, Low\_B.Low\_W.glo, Date],}
\CommentTok{\#          col = "blue",}
\CommentTok{\#          ylim = ylim)}
\CommentTok{\#   points(temp[, wattGLB, Date], col = "green")}
\CommentTok{\#   title(as.Date(ad, origin = "1970{-}01{-}01"))}
\CommentTok{\# \}}
\end{Highlighting}
\end{Shaded}

>>>>

  pdftitle={Enhancement of SDR in Thessaloniki Clear Sky},

@@

\title{Enhancement of SDR in Thessaloniki Clear Sky}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-09}

@@

$objective
[1] 8619.603
\end{verbatim}

@@

\NormalTok{ylim }\OtherTok{\textless{}{-}} \FunctionTok{range}\NormalTok{(DTyear[, glo, GLB])}
\end{Highlighting}
\end{Shaded}

\subsection{Relations}\label{relations}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-20} \end{center}

\begin{verbatim}
$minimum
[1] 0.8593852

$objective
[1] 0.6165028
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-21} \end{center}

\begin{verbatim}
[1] 0.6615997
\end{verbatim}

\subsection{Yearly values}\label{yearly-values}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-4} \end{center}

\begin{verbatim}
$mae
[1] 97.0816

$mse
[1] 9657.575

$rmse
[1] 98.27296

$mape
[1] 0.1672027

$nmse
[1] 45.49449

$rstd
[1] 0.1688189
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-5} \end{center}

@@
